Weed and Corn segmentation through Convolutional Neuronal Networks

### 2017-07-04 PaperBCJ.tex
data

Once we completed the processing of the images were obtained 2369 images of Maize and 632 images of Weed, \textbf{Seng} \cite{SengChang} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, because we will develop a  system  for classify the maize in any position , we considered to rotate the source sample to 90º,180º and 270º so the dataset will be treble, improving the accuracy of the model. \\

@@

>>>>

Once we completed the processing of the images were obtained 2369 images of Maize and 632 images of Weed, \textbf{Seng} \cite{SengChang} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, in addition \cite{Sladojevic}  they measure that this allows to reduce the overfitting and to improve the presicion in the training, reason why we use rotations that go from the 30 to the 330 degrees in steps of 30, obtaining in this way to increase The date for 12 times and have better chances of recognizing plants that are in any orientation. \\

@@

\bibitem{Sladojevic}
S. Sladojevic,M. Arsenovic, A. Andarela, D. Culibrk and D, Stefanovic, \emph{Deep Neural Networks Based Recognition Diseases by Leaf Image Classification \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Trento, Italy: Srdjan Sladojevic, 2016.
